A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-14 Paper/Manuscript.Rmd
Add limitations, standardize fig size

## Violin plot example
Figure \@ref(fig:petalwidths) shows petal widths by iris type.

``` {r petalwidths, message=FALSE, fig.width = 6, fig.height = 4, fig.cap = "Petal widths by class" }
df %>%
    ggplot() + 
    geom_violin(aes( x = iris_class, y = petal_width, color = iris_class), draw_quantiles = T, trim = F, show.legend = F) +
    geom_boxplot(aes( x = iris_class, y = petal_width, color = iris_class), width = 0.07, show.legend = F)+
    ggtitle("Petal widths by species") +
    scale_color_manual(values=cal_palette4)

@@

# Limitations
It is important to include a discussion of limitations in any paper. Limitations of this template include:

- Figures are included after the text, not at the location where they are discussed in the text

>>>>

## Violin plot example
Figure \@ref(fig:petalwidths) shows petal widths by iris type.
``` {r petalwidths, message=FALSE, fig.width = 8, fig.height = 4.5, fig.cap = "Iris petal widths by species" }
df %>%
    ggplot() + 
    geom_violin(aes( x = iris_class, y = petal_width, color = iris_class), draw_quantiles = T, trim = F, show.legend = F) +
    geom_boxplot(aes( x = iris_class, y = petal_width, color = iris_class), width = 0.07, show.legend = F)+
    scale_color_manual(values=cal_palette4)

@@

# Limitations
It is important to include a discussion of limitations in any paper. Some limitations of this template include:

- Whether or not figures are included inline with text appears to depend of the version of LaTeX the document is compiled with. Compiling on a computer where TinyTeX is installed (eg in the Binder associated with the reporsitory for this project on GitHub) will render the figures inline, whereas compiling the same document on a Windows computer with MikTeX installed does not
- Does not include instructions on how to align figures
